---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```
# arpr

<!-- badges: start -->
<!-- badges: end -->

The goal of arpr is to provide convenience functions for programming with magrittr pipes. Conditional pipes, a string prefixer and a function to pipe the given object into a specific argument given by character name are currently supported. It is named after the dadaist Hans Arp, a friend of Rene Magritte.


_Note that the {arpr} package was originally created by [Jirka Lewandowski](https://github.com/jirkalewandowski). The present repository is a fork to be able to continue development of this package, required for [{gitlabr}](https://github.com/statnmap/gitlabr)._  

## Installation

You can install the released version of arpr from [CRAN](https://CRAN.R-project.org) with:

``` r
install.packages("arpr")
```

And the development version from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("statnmap/arpr")
```

## Examples

```{r}
library(arpr)
```


- Prefix a string of text 

```{r}
"xyz" %>%
   prefix("abc")
```

- `iff()` applies a function if and only if test is TRUE
  + otherwise return input value unchanged
  + `iffn()` is if and only if test is FALSE

```{r}
x <- sample(c(1, 2, NA), 1)
x
x <- x %>%
  iff(is.na, const(0))
x

x <- sample(c(1, 2, NA), 1)
x
x %>%
  iff(x <= 0, function(x) { x - 2 })

x <- sample(c(1, 2, NA), 1)
x
x %>%
  iffn(is.na, exp)
```

-  Pipe into specific formal argument

```{r}
5L %>%
  pipe_into("digits", format, 2.731234567)
```

